Footpath Planning for Example-driven Procedural Road Networks

### 2020-04-14 paper/paper.tex
Include image with example turning funciton in report
Remove interactive constraint from report

\begin{enumerate}
\item The road network is assumed to be a 2D simple graph. This means that any overlapping roads, such as tunnels and bridges that cross over street-level roads, will be eliminated from the training set. Any self-connected nodes will also be eliminated from the training set.
\item It will be assumed that the city map consists of only arterial (primary) roads, secondary roads and footpaths.
\item It will be assumed that the primary, secondary and tertiatry roads all have a fixed width. Primary roads have a set width, and secondary roads and footpaths as well.
\item It will be assumed that the use case of the application is for generating areas with the size of a neighbourhood or a few city blocks. The area that the user will sketch will typically be around 0.1 km2.
\item The program will not handle terrain features and altitude. It will be assume that the road mesh is projected on a flat 2D surface.
\end{enumerate}

@@

>>>>

\begin{enumerate}
\item The road network is assumed to be a 2D simple graph. This means that any overlapping roads, such as tunnels and bridges that cross over street-level roads, will be eliminated from the training set. Any self-connected nodes will also be eliminated from the training set.
\item It will be assumed that the city map consists of only arterial (primary) roads, secondary roads and footpaths.
\item It will be assumed that the primary, secondary and tertiatry roads all have a fixed width. Primary roads have a set width, and secondary roads and footpaths as well.
\item The program will not handle terrain features and altitude. It will be assume that the road mesh is projected on a flat 2D surface.
\end{enumerate}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_turn_function}
    \caption{An example of the turning function of a polygon.}
    \label{fig:space}
\end{figure}
